%-------------------------
% Resume in Latex
% Author : Ismael Abreu
% Based on: Wilmer Gonzalez
% License : MIT
%------------------------

\documentclass[11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{xcolor}


% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands
\newcommand{\resumeItem}[1]{%2
  \item\small{
    %\textbf{#1}
    #1
    %{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemSub}[1]{%2
  \item[--]\small\textit{#1}
}


\newcommand{\sepsection}{\vspace{16pt}}



\newcommand{\resumeSubheading}[4]{
  \vspace{12pt}\item%-1
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small \color{gray} #2} \\
      \textit{\small #3} & \textit{\color{gray} \small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \vspace{12pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\color{gray} \small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemi}{\ding{}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=6pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
 \textbf{#1:} #2
}

% COLOR THEMES SELECTION
% For Light theme un-comment this and comment the Dark theme section below

\colorlet{urlcolor}{blue}


\newcommand{\latestVersion}{\href{https://github.com/ismaelga/resume/raw/main/ismael_abreu_resume.pdf}{Get Latest version}}
\newcommand{\website}{}

% For Dark theme un-comment this and comment the Light theme section above

% \colorlet{textcolor}{white!80!gray}
% \colorlet{backgroundcolor}{black!30!gray}
% \colorlet{urlcolor}{blue!25!white}
% \AtBeginDocument{\color{textcolor}}
% \newcommand{\otherThemeRef}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_light.pdf}{See light theme}}
% \newcommand{\latestVersion}{\href{https://github.com/wilmeragsgh/resume/raw/master/wilmer_gonzalez_dark.pdf}{Get Latest version}}
% ---

% DOCUMENT MAIN
\begin{document}

% For Dark theme also un-comment this line:
% \pagecolor{backgroundcolor}

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linktr.ee/ismga}{\Large Ismael Gonçalves Abreu}} &
  \href{https://linktr.ee/ismga}{ \faicon{link} \color{urlcolor} https://linktr.ee/ismga } \\
  \href{mailto:me@ismaelga.com}{me@ismaelga.com} & 
  \href{https://github.com/ismaelga}{ \faicon{github} \color{urlcolor} ismaelga} \\
  & Porto, Portugal \\
  \textsl{\small \latestVersion} & \faicon{code} Elixir, Ruby, TypeScript, Python
  
\end{tabular*}
% ---

% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Coinlever}{(remote) Portugal}
      {Senior Software Engineer}{2021 - 2023}
      \resumeItemListStart
        \resumeItemSub{Small team working on a privately owned platform to manage Crypto portfolios, connected to multiple exchanges to facilitate running tailored trading strategies}
        \resumeItem{
        Worked on the platform, fixing bugs, developed new features including integration of new exchanges \textbf{Elixir, Phoenix, Elm, Postgres, Fireblocks, GCP}}
        \resumeItem{
        Designed and implemented the architecture for a new system that leveraged AI based algorithms to automate portfolio management \textbf{Python, serverless, Dynamodb, AWS}}
        
      \resumeItemListEnd
\sepsection

    \resumeSubheading
      {Glazed Developers}{(remote) Porto, Portugal}
      {Senior Full-Stack Developer}{2015-2021}

      \resumeSubSubheading
      {LVMH}{(remote) London/Paris 2018-2020}
      \resumeItemListStart
        \resumeItemSub{Worked on the group's digital department developing new technology solutions for luxury brands like, Rimowa, Guerlain, Fendi and Celine.}
        \resumeItem{Designed and built a framework to reduce the time and effort implementing AI conversion assistants \textbf{Typescript, NLP, IBM Watson, Nodejs, SQS, AI}}
        \resumeItem{Built conversation assistants for multiple LVMH's brands, for costumer services, recommendations, product discovery, ...}
        \resumeItem{Built an APP to manage copy for the chatbots, including translations. \textbf{Elixir, Phoenix, GraphQL}}    
        \resumeItem{Built the Front-end for in-store customer care surveys, with offline capabilities. \textbf{React, Typescript}}
        \resumeItem{Worked with DevOps team to design and implement a new infra tailored for the needs including CI/CD. \textbf{Kubernetes, GitOps, AWS, Jenkins}}
      \resumeItemListEnd

      \resumeSubSubheading{\href{https://mercadao.pt}{Mercadão}}{Porto 2020}
      \resumeItemListStart
        \resumeItemSub{Grocery delivery Start-up bought by one of the biggest chain in Portugal}
        \resumeItem{Maintenance work and fixed scaling issues. \textbf{AngularJS, IBM Loopback, MongoDB}}
      \resumeItemListEnd

      \resumeSubSubheading
      {\href{https://wechangers.org}{WeChangers}}{Porto 2016-2017 and 2020-2021}
      \resumeItemListStart
        \resumeItemSub{Start-up building an online network for Social Impact people, organizations and projects, for example non-profit Orgs trying to solve water supply issues}
        \resumeItem{Built the product and platform from scratch, including a lot of work on early on specification. \textbf{Ruby on Rails, Redis, React, Postgres, Azure}}
        \resumeItem{Mentored a Mid Software Developer. \textbf{Ruby on Rails, Redis, React, Postgres, Azure}}
        \resumeItem{Created tools for managing awards, challenges, contests, calls and grants. \textbf{TypeScript, React, Next.js}}
        \resumeItem{Participated in interviews to find candidates to work for Wechangers.}
      \resumeItemListEnd
      
      \resumeSubSubheading
      {\href{https://farfetch.com/}{FARFETCH}}{Porto 2018}
      \resumeItemListStart
        \resumeItemSub{Number 1 online marketplace for luxury fashion brands}
        \resumeItem{Built a white label version of their main e-commerce site for big brands that want to sell on their own website. \textbf{Nodejs, React, RethinkDB, Express.js, Flux, Redux}}
        \resumeItem{Built a component blocks based custom page builder. Including maintainemce of the open-source library used for this, reaching 200 stars on github \textbf{Nodejs, React, JSON schema, \href{https://github.com/ismaelga/react-json-editor}{react-json-editor}}}
      \resumeItemListEnd

       

      \resumeSubSubheading
      {\href{https://www.dontdrivedirty.com}{QuickQuak Car wash}}{(remote) USA 2015}
      \resumeItemListStart
        \resumeItemSub{Large USA based car wash chain with 200+ locations}
        \resumeItem{Early development of the back-end API for their new POS system to be used on all their locations. \textbf{Ruby on Rails, Postgres, Digital Ocean}}
      \resumeItemListEnd

\sepsection

\resumeSubheading
      {\href{https://web.archive.org/web/20190811141419/http://www.nmusic.pt/}{Nmusic} - Software Developer}{Porto}
      {Backend Developer}{2014-2015}
      \resumeItemListStart
      \resumeItemSub{Music streaming service, providing Meo Music for one of the largest Portuguese telecom companies, Meo (Altice group)}
      \resumeItem{Worked on the back-end and content ingestion system. \textbf{Ruby on Rails,  Postgresql, Redis, ElasticSearch, Solr, AWS}}
      \resumeItem{Built a "light" client version and allow 3G data subscriptions and download of music tracks. \textbf{Ruby, Sinatra}}
      \resumeItem{Developed a proof of concept music recommender system based on ElasticSearch scoring. \textbf{ElasticSearch, Rust}}
      \resumeItemListEnd

\sepsection
\resumeSubheading
      {Waverise}{Porto}
      {Full-Stack Developer}{2013}
      \resumeItemListStart
        \resumeItemSub{Consultancy firm working mainly for London based clients.}
        \resumeItem{Developed a system for Human Resources management for the health industry. Shifts and off-time management for medical personnel \textbf{Ruby, JavaScript, JQuery, Postgres, Resque}}
        \resumeItem{Created a real-time interactions service, to be used in conferences, with multiple channels of communication, SMS, tweeter, Facebook, Email, HTTP API, ... \textbf{Ruby, JavaScript, Twillio}}
      \resumeItemListEnd
\sepsection
\resumeSubheading
      {Sinemys}{Porto}
      {Full-Stack Developer}{2012}
      \resumeItemListStart
        \resumeItemSub{Start-up consultancy firm devoping parts of \href{https://www.bwizer.com/pt/}{Bwizer}'s marketing tools to promote their courses.}
        \resumeItem{Developed some websites and built automation to post content in multiple online afvertising platforms. \textbf{Ruby, JavaScript, jQuery, Casper.js}}
      \resumeItemListEnd
\resumeSubHeadingListEnd
% \newpage

% ---
\phantom{TypeScript, Nodejs, React, Redux, Next.js, Nginx, Luadns, JWT, SOAP, NLP, GraphQL, TDD,  AWS(Lambda, S3, SQS), Azure, Google Cloud(GKE), Postgres, MongoDB, RethinkDB, Redis, ElasticSearch, Dynamodb, Ruby on Rails, Sinatra, Sidekiq, Python, OTP, Phoenix, Phoenix Liveview, GenStage, Oban, Postgres, MongoDB, RethinkDB, Redis, ElasticSearch, Dynamodb}


\sepsection

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidade do Minho}{Braga, Portugal}
      {B.Sc in Technologies and Information Systems}{2012}
  \resumeSubHeadingListEnd
% ---

\sepsection

% CERTIFICATIONS
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
     {Online Courses}{}{}{}
    \resumeSubSubheading
    {Software Engineering for SaaS, University of California, Berkeley/Coursera}{Issued  2012}
    \resumeSubSubheading
     {Functional Principles in Scala, École Polytechnique Fédérale de Lausanne/Coursera}{Issued 2013}
    \resumeSubSubheading
     {Software as a Service, BerkeleyX/EDX}{Issued 2012}
     
\resumeSubHeadingListEnd
  

\sepsection

% PROGRAMMING SKILLS

\section{Other programming tools}
  \resumeSubHeadingListStart
  
  \resumeSubItem{\textbf{Javascript} TypeScript, Nodejs, React, Redux, Next.js}
  
  \resumeSubItem{\textbf{Ruby} Ruby on Rails, Sinatra, Sidekiq}
  
  \resumeSubItem{\textbf{Elixir:} OTP, Phoenix, Phoenix Liveview, GenStage, Oban}
  
  \resumeSubItem{\textbf{DBs:} Postgres, MongoDB, RethinkDB, Redis, ElasticSearch, Dynamodb}
  
  \resumeSubItem{\textbf{Cloud services:} AWS(Lambda, S3, SQS), Azure, Google Cloud(GKE)}
  
  \resumeSubItem{\textbf{Other tools:} Nginx, Luadns, JWT, SOAP, NLP, GraphQL, TDD}
  
  \resumeSubItem{\textbf{Familiar Languages:} Elm, ReasonML, Go, Rust}

  \resumeSubItem{\textbf{Tools:} Slack, Jira, Linux, MacOS, VS Code, Neovim, Git, Github, Asana}
  
  \resumeSubHeadingListEnd


% ---
\end{document}
